Unnecessarily Complicated Research Title

### 2020-10-29 Chapter4/4_4_results.tex
chapter_4_passed

In this section, we first present temporal characterization of the three services (Section~\ref{sec:temporal_characterization}). Then, we describe the services spatial-temporal characteristics (Section~\ref{sec:spatial-temporal}). Finally, we present users' behavior (Section~\ref{sec:user-behavior}).

\subsection{Temporal characteristics}\label{sec:temporal_characterization}

\begin{figure}
	\centering
	\subfloat[\centering Two-way Modo Weekdays]{{\includegraphics[width=0.46\columnwidth]{modo_inTravel/weekdays.pdf}} \label{fig:modo_wd}}%
	\qquad
	\subfloat[\centering Two-way Modo Weekends]{{\includegraphics[width=0.46\columnwidth]{modo_inTravel/weekends.pdf}} \label{fig:modo_we}}%
	\caption{Modo Minute-by-minute mean value (plus/minus standard deviation) for  the  percentage of busy (blue curve) and reserved cars (red curve), for weekdays and weekends}
	\label{fig:4_4_modo_busy}%
\end{figure}

\begin{figure}
	\centering
	\subfloat[\centering One-way Evo Weekdays]{{\includegraphics[width=0.46\columnwidth]{evo_inTravel/weekdayslim.pdf}} \label{fig:evo_wd}}%
	\qquad
	\subfloat[\centering One-way Evo Weekends]{{\includegraphics[width=0.46\columnwidth]{evo_inTravel/weekendslim.pdf}} \label{fig:evo_we}}%
	\caption{Evo Minute-by-minute mean value (plus/minus standard deviation) for  the  percentage of busy (blue curve) and reserved cars (red curve), for weekdays and weekends}
	\label{fig:4_4_evo_busy}%
\end{figure}

\begin{figure}
	\centering
	\subfloat[\centering Free floating car2Go Weekdays]{{\includegraphics[width=0.46\columnwidth]{car2go_inTravel/weekdayslim.pdf}} \label{fig:c2g_wd}}%
	\qquad
	\subfloat[\centering Free floating car2Go Weekends]{{\includegraphics[width=0.46\columnwidth]{car2go_inTravel/weekendslim.pdf}} \label{fig:c2g_we}}%
	\caption{car2go Minute-by-minute mean value (plus/minus standard deviation) for  the  percentage of busy (blue curve) and reserved cars (red curve), for weekdays and weekends}
	\label{fig:4_4_c2g_busy}%
\end{figure}

%PRENSENTATION OF FIGURE
Figures~\ref{fig:4_4_modo_busy}, \ref{fig:4_4_evo_busy} and \ref{fig:4_4_c2g_busy} show the service daily demand pattern. In all plots, the blue and red solid lines refer to a minute-by-minute mean value over the studied period for the percentage of busy and reserved cars, respectively, for each service. The plots show also the standard deviation from the mean as the smoothed gray and orange background areas around the mean. On the left of each pair of figures (figures \ref{fig:modo_wd}, \ref{fig:evo_wd} and \ref{fig:c2g_wd}) is presented the demand pattern during working days, while on the (figures \ref{fig:modo_we}, \ref{fig:evo_we} and \ref{fig:c2g_we}) is shown the demand for weekends (Saturdays, Sundays, and festivities).

@@

\begin{figure}[htb]
\centering
    \begin{minipage}[b]{0.45\linewidth}
    \centering
     \includegraphics[width=59mm]{modo_cdfs/modo_tarde_noiteCDF_rebuttal.pdf}
     {\\(a) Two-way Modo}
    \end{minipage}
    \hspace{5mm}
    \begin{minipage}[b]{0.45\linewidth}
     \centering
     \includegraphics[width=65mm]{evo_cdfs/evo_tarde_noiteCDF_rebuttal.pdf}
     \vspace*{-3mm}
     {\\(b) One-way Evo}
    \end{minipage}
    %\hspace{1cm}
    %\hspace{5mm}
    \begin{minipage}[b]{0.45\linewidth}
    \vspace{5mm}
     \centering
     \includegraphics[width=65mm]{car2go_cdfs/c2g_tarde_noiteCDF_rebuttal.pdf}
     {\\(c) Free floating Car2Go}
    \end{minipage}
    \caption{Cumulative distribution function of vehicle busy time during a weekday.}
    \label{fig:cdfs_picos}
\end{figure}

%DESCRIPTION OF FIGURE
Figure~\ref{fig:cdfs_picos} presents the Empirical Cumulative Distribution Function (ECDF) of vehicles busy time, i.e., the rental duration, during load peaks of the day. In this case, we evaluate the load periods from 7~AM to 10~AM and from 4~PM to 8~PM for free-floating and one-way, from 11~AM to 4~PM and 7~PM to 8~PM for two-way, and also all-day data for the three services.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial-temporal characteristics}
\label{sec:spatial-temporal}

%modo
\begin{figure}[hhh!!]
\centering
   \begin{minipage}[b]{0.3\linewidth}
   \centering      
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.9cm}
           \centering
           \includegraphics[width=42mm]{modo_heatmaps/min/0.pdf}
           {\\(a) 0~AM to 1~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/8.pdf}
           {\\(c) 8~AM to 9~AM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/16.pdf}
           {\\(e) 4~PM to 5~PM}
         \end{minipage}
   \end{minipage}
   \hspace{3mm}
   \begin{minipage}[b]{0.3\linewidth}
   \centering
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/4.pdf}
           {\\(b) 4~AM to 5~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/12.pdf}
           {\\(d) 12~AM to 1~PM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.1cm}
           \centering
           \includegraphics[width=42mm]{modo_heatmaps/min/20.pdf}
           {\\(f) 8~PM to 9~PM}
         \end{minipage}
   \end{minipage}
   \begin{minipage}[b]{0.1\linewidth}
   \centering
   		 \hspace*{12mm}
   		 \includegraphics[width=12mm]{modo_heatmaps/legenda_modo.pdf}
         \vspace{17mm}
   \end{minipage}
   %\hspace{1cm}
   \caption{Spatial-temporal service demand for two-way service Modo.}
   \label{fig:heat_modo}
\end{figure}

%evo
% Não é o definitivo
\begin{figure}[hhh!!]
\centering
   \begin{minipage}[b]{0.3\linewidth}
   \centering      
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.9cm}
           \centering
           \includegraphics[width=42mm]{evo_heatmaps/min/hora0.pdf}
           {\\(a) 0~AM to 1~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora8.pdf}
           {\\(c) 8~AM to 9~AM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora16.pdf}
           {\\(e) 4~PM to 5~PM}
         \end{minipage}
   \end{minipage}
   \hspace{3mm}
   \begin{minipage}[b]{0.3\linewidth}
   \centering
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora4.pdf}
           {\\(b) 4~AM to 5~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora12.pdf}
           {\\(d) 12~AM to 1~PM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.1cm}
           \centering
           \includegraphics[width=42mm]{evo_heatmaps/min/hora20.pdf}
           {\\(f) 8~PM to 9~PM}
         \end{minipage}
   \end{minipage}
   \begin{minipage}[b]{0.1\linewidth}
   \centering
   		 \hspace*{12mm}
   		 \includegraphics[width=12mm]{evo_heatmaps/legenda_evo.pdf}
         \vspace{17mm}
   \end{minipage}
   %\hspace{1cm}
   \caption{Spatial-temporal service demand for one-way service Evo.}
   \label{fig:heat_evo}
\end{figure}

% car2go
\begin{figure}[hhh!!]
\centering
   \begin{minipage}[b]{0.3\linewidth}
   \centering      
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.9cm}
           \centering
           \includegraphics[width=42mm]{car2go_heatmaps/min/0.pdf}
           {\\(a) 0~AM to 1~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/8.pdf}
           {\\(c) 8~AM to 9~AM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/16.pdf}
           {\\(e) 4~PM to 5~PM}
         \end{minipage}
   \end{minipage}
   \hspace{3mm}
   \begin{minipage}[b]{0.3\linewidth}
   \centering
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/4.pdf}
           {\\(b) 4~AM to 5~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/12.pdf}
           {\\(d) 12~AM to 1~PM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.1cm}
           \centering
           \includegraphics[width=42mm]{car2go_heatmaps/min/20.pdf}
           {\\(f) 8~PM to 9~PM}
         \end{minipage}
   \end{minipage}
   \begin{minipage}[b]{0.1\linewidth}
   \centering
   		 \hspace*{12mm}
   		 \includegraphics[width=12mm]{car2go_heatmaps/legenda_car2go.pdf}
         \vspace{17mm}
   \end{minipage}
   %\hspace{1cm}
   \caption{Spatial-temporal service demand for free-floating service Car2Go.}
   \label{fig:heat_car2go}
\end{figure}

Figures~\ref{fig:heat_modo}, \ref{fig:heat_evo} and \ref{fig:heat_car2go} present heat-maps of the hourly\footnote{Due to space constraints, we only show one-hour period every four hour.} mean number of busy vehicles in a given location, considering analyzed period. In the case of Modo, a location refers to a fixed station. In the case of the other two services, the maps present clustered travel records where users pick-up or leave a vehicle. To cluster these points the algorithm uses a 400\,m radius as a reference, forming a region close to a neighborhood. Rangin radius from 100\,m to 1000\,m, leads to similar results.

@@

Figures~\ref{fig:matrixEvo} and \ref{fig:matrixCar2Go} detail the spatial-temporal demand for Evo and Car2Go by presenting their origin-destination matrix mapped on 31 city areas as defined by the metropolitan city of Vancouver. To enhance the visual effects, we normalized the previous heat-maps values to a scale between 0-1, using the min-max method. Moreover, due to space constraint, this work shows the origin-destination matrix at a specific hour, i.e., at 4\,PM.
In general, the users tend to start and end a trip at the same location. It appears that during working days, users tend to use a shared car  returning it to the same region where they start (likely where they are working or living). However, for both services, a non-negligible probability to spread services along all city area is noticeable. 
Moreover, we also note that some regions serve as hubs. This is more notable for Evo service. As shown in Figure~\ref{fig:matrixEvo}, the downtown area serves as a hub to start trips to almost all other regions. The opposite (a high tendency to start a trip ending at downtown) trend is not present. As a consequence, service may become unbalanced and, from time to time, service maintenance should relocate vehicles from a region to another, to accommodate the daily demand.

\begin{figure}[tbh]
\centering
\includegraphics[width=0.85\columnwidth]{destination_matrix/hour16.png}
\caption{Origin-destination matrix for one-way service Evo (from 4~PM to 5~PM).}
\label{fig:matrixEvo}
\end{figure}
%
\begin{figure}[tbh]
\centering
\includegraphics[width=0.85\columnwidth]{car2go_destination_matrix/hour16.png}
\caption{Origin-destination matrix for free-floating service Car2Go (from 4~PM to 5~PM).}
\label{fig:matrixCar2Go}
\end{figure}

@@

\subsection{User behavior characteristics}
\label{sec:user-behavior}

@@

Figure~\ref{fig:busy_all_eCDF} shows the Cumulative Distribution Function of vehicle busy time.  Modo, Evo and Car2Go busy time and their best statistical distribution fitting are shown in blue, red and yellow, respectively. For all three services, the Inverse~Gamma\footnote{Cumulative distribution function (CDF) of the Inverse~Gamma distribution: $F(x, a, \beta, \delta) = \frac{1}{\Gamma(a)}\int_{1/\left((x-\beta)/\delta\right)}^{\infty}t^{a-1}e^{-t}dt$}, 
the Burr\footnote{Cumulative distribution function (CDF) of the Burr distribution: $F(x,c,d,\beta,\delta)=\left(1 + \left((x-\beta)/\delta\right)^{-c}\right)^{-d}$}, 
and Mielke's Beta-Kappa\footnote{Cumulative distribution function (CDF) of the Mielke's Beta-Kappa distribution: $F(x,k,s,\beta,\delta) = \frac{\left((x-\beta)/\delta\right)^{k}}{(1+\left((x-\beta)/\delta\right)^{s})^{(k*\frac{1}{s})}}$} 
distributions present a  good fitting to the empirical data, with similar MLEs.  
Table~\ref{table:fit_busy} summarizes the parameters of the distributions of the busy time for each statistical distribution.
Despite all three services present the same statistical distribution fitting, 
the two-way service (i.e., Modo), presents a clear shift to right on its curve when compared to the other two services, as shown in Figure~\ref{fig:busy_all_eCDF}. As we previously discussed, the median busy time on Modo is more than one hour longer than the median busy time for the other services. 
Users in Modo must return cars to the same station they originated travels. As a consequence, they tend to perform longer tasks. On the other hand, with the other two services users tend to do a longer number of shorter travels.

Finally, Figure~\ref{fig:idle_all_eCDF}, presents vehicle idle periods distribution.  Power~log~normal\footnote{Cumulative distribution function (CDF) of the Power~log~normal distribution: $F(x,c,s,\beta,\delta)=1-\left(\frac{1}{\sqrt{2\pi}}\int_{-\infty}^{-log((x-\beta)/\delta)/s}e^{-t^{2}/2}dt\right)^{c}$}, Burr and Mielke's~Beta$-$Kappa distributions best fit the idle data, for all three datasets. Table~\ref{table:fit_idle} presents the distribution parameters. 
Again, Modo presents a distinct behavior from the other two services. The longer idle period for Modo vehicles corroborates to our previous observations. Indeed, the demand for car-sharing varies over the city during a day. While users in Evo and Car2Go can park anywhere, they contribute to spreading cars over the city. For example, at least 75\% of cars in Modo remains idle for periods longer than 2 hours. For the other two services, no more than 20\% of vehicles remains idle for the same period.

@@

\begin{figure}[tbh]
   \centering
   \includegraphics[width=0.85\columnwidth]{images_test/CDF_Fit_final.pdf}
   \caption{Cumulative distribution function of vehicle busy time.}
   \label{fig:busy_all_eCDF}
\end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=0.85\columnwidth]{images_test/CDF_Fit_idle_final.pdf}
   \caption{Cumulative distribution function of vehicle idle time}
   \label{fig:idle_all_eCDF}
\end{figure}

>>>>

In this section, we first present temporal characterization of the three services (section~\ref{sec:4_4_temporal_characterization}). Then, we describe the services spatial-temporal characteristics (section~\ref{sec:4_4_spatial-temporal}). Finally, we present users' behavior (section~\ref{sec:4_4_user-behavior}).

\subsection{Temporal characteristics}
\label{sec:4_4_temporal_characterization}

\begin{figure}
	\centering
	\subfloat[\centering Two-way Modo Weekdays]{{\includegraphics[width=0.46\columnwidth]{modo_inTravel/weekdays.pdf}} \label{fig:4_4_modo_wd}}%
	\qquad
	\subfloat[\centering Two-way Modo Weekends]{{\includegraphics[width=0.46\columnwidth]{modo_inTravel/weekends.pdf}} \label{fig:4_4_modo_we}}%
	\caption{Modo Minute-by-minute mean value (plus/minus standard deviation) for  the  percentage of busy (blue curve) and reserved cars (red curve), for weekdays and weekends}
	\label{fig:4_4_modo_busy}%
\end{figure}

\begin{figure}
	\centering
	\subfloat[\centering One-way Evo Weekdays]{{\includegraphics[width=0.46\columnwidth]{evo_inTravel/weekdayslim.pdf}} \label{fig:4_4_evo_wd}}%
	\qquad
	\subfloat[\centering One-way Evo Weekends]{{\includegraphics[width=0.46\columnwidth]{evo_inTravel/weekendslim.pdf}} \label{fig:4_4_evo_we}}%
	\caption{Evo Minute-by-minute mean value (plus/minus standard deviation) for  the  percentage of busy (blue curve) and reserved cars (red curve), for weekdays and weekends}
	\label{fig:4_4_evo_busy}%
\end{figure}

\begin{figure}
	\centering
	\subfloat[\centering Free floating car2Go Weekdays]{{\includegraphics[width=0.46\columnwidth]{car2go_inTravel/weekdayslim.pdf}} \label{fig:4_4_c2g_wd}}%
	\qquad
	\subfloat[\centering Free floating car2Go Weekends]{{\includegraphics[width=0.46\columnwidth]{car2go_inTravel/weekendslim.pdf}} \label{fig:4_4_c2g_we}}%
	\caption{car2go Minute-by-minute mean value (plus/minus standard deviation) for  the  percentage of busy (blue curve) and reserved cars (red curve), for weekdays and weekends}
	\label{fig:4_4_c2g_busy}%
\end{figure}

%PRENSENTATION OF FIGURE
Figures~\ref{fig:4_4_modo_busy}, \ref{fig:4_4_evo_busy} and \ref{fig:4_4_c2g_busy} show the service daily demand pattern. In all plots, the blue and red solid lines refer to a minute-by-minute mean value over the studied period for the percentage of busy and reserved cars, respectively, for each service. The plots show also the standard deviation from the mean as the smoothed gray and orange background areas around the mean. On the left of each pair of figures (figures \ref{fig:4_4_modo_wd}, \ref{fig:4_4_evo_wd} and \ref{fig:4_4_c2g_wd}) is presented the demand pattern during working days, while on the (figures \ref{fig:4_4_modo_we}, \ref{fig:4_4_evo_we} and \ref{fig:4_4_c2g_we}) is shown the demand for weekends (Saturdays, Sundays, and festivities).

@@

\begin{figure}[htb]
\centering
    \begin{minipage}[b]{0.45\linewidth}
    \centering
     \includegraphics[width=59mm]{modo_cdfs/modo_tarde_noiteCDF_rebuttal.pdf}
     {\\(a) Two-way Modo}
    \end{minipage}
    \hspace{5mm}
    \begin{minipage}[b]{0.45\linewidth}
     \centering
     \includegraphics[width=65mm]{evo_cdfs/evo_tarde_noiteCDF_rebuttal.pdf}
     \vspace*{-3mm}
     {\\(b) One-way Evo}
    \end{minipage}
    %\hspace{1cm}
    %\hspace{5mm}
    \begin{minipage}[b]{0.45\linewidth}
    \vspace{5mm}
     \centering
     \includegraphics[width=65mm]{car2go_cdfs/c2g_tarde_noiteCDF_rebuttal.pdf}
     {\\(c) Free floating Car2Go}
    \end{minipage}
    \caption{Cumulative distribution function of vehicle busy time during a weekday.}
    \label{fig:4_4_cdfs_picos}
\end{figure}

%DESCRIPTION OF FIGURE
Figure~\ref{fig:4_4_cdfs_picos} presents the Empirical Cumulative Distribution Function (ECDF) of vehicles busy time, i.e., the rental duration, during load peaks of the day. In this case, we evaluate the load periods from 7~AM to 10~AM and from 4~PM to 8~PM for free-floating and one-way, from 11~AM to 4~PM and 7~PM to 8~PM for two-way, and also all-day data for the three services.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial-temporal characteristics}
\label{sec:4_4_spatial-temporal}

%modo
\begin{figure}[hhh!!]
\centering
   \begin{minipage}[b]{0.3\linewidth}
   \centering      
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.9cm}
           \centering
           \includegraphics[width=42mm]{modo_heatmaps/min/0.pdf}
           {\\(a) 0~AM to 1~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/8.pdf}
           {\\(c) 8~AM to 9~AM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/16.pdf}
           {\\(e) 4~PM to 5~PM}
         \end{minipage}
   \end{minipage}
   \hspace{3mm}
   \begin{minipage}[b]{0.3\linewidth}
   \centering
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/4.pdf}
           {\\(b) 4~AM to 5~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{modo_heatmaps/min/12.pdf}
           {\\(d) 12~AM to 1~PM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.1cm}
           \centering
           \includegraphics[width=42mm]{modo_heatmaps/min/20.pdf}
           {\\(f) 8~PM to 9~PM}
         \end{minipage}
   \end{minipage}
   \begin{minipage}[b]{0.1\linewidth}
   \centering
   		 \hspace*{12mm}
   		 \includegraphics[width=12mm]{modo_heatmaps/legenda_modo.pdf}
         \vspace{17mm}
   \end{minipage}
   %\hspace{1cm}
   \caption{Spatial-temporal service demand for two-way service Modo.}
   \label{fig:4_4_heat_modo}
\end{figure}

%evo
% Não é o definitivo
\begin{figure}[hhh!!]
\centering
   \begin{minipage}[b]{0.3\linewidth}
   \centering      
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.9cm}
           \centering
           \includegraphics[width=42mm]{evo_heatmaps/min/hora0.pdf}
           {\\(a) 0~AM to 1~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora8.pdf}
           {\\(c) 8~AM to 9~AM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora16.pdf}
           {\\(e) 4~PM to 5~PM}
         \end{minipage}
   \end{minipage}
   \hspace{3mm}
   \begin{minipage}[b]{0.3\linewidth}
   \centering
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora4.pdf}
           {\\(b) 4~AM to 5~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{evo_heatmaps/min/hora12.pdf}
           {\\(d) 12~AM to 1~PM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.1cm}
           \centering
           \includegraphics[width=42mm]{evo_heatmaps/min/hora20.pdf}
           {\\(f) 8~PM to 9~PM}
         \end{minipage}
   \end{minipage}
   \begin{minipage}[b]{0.1\linewidth}
   \centering
   		 \hspace*{12mm}
   		 \includegraphics[width=12mm]{evo_heatmaps/legenda_evo.pdf}
         \vspace{17mm}
   \end{minipage}
   %\hspace{1cm}
   \caption{Spatial-temporal service demand for one-way service Evo.}
   \label{fig:4_4_heat_evo}
\end{figure}

% car2go
\begin{figure}[hhh!!]
\centering
   \begin{minipage}[b]{0.3\linewidth}
   \centering      
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.9cm}
           \centering
           \includegraphics[width=42mm]{car2go_heatmaps/min/0.pdf}
           {\\(a) 0~AM to 1~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/8.pdf}
           {\\(c) 8~AM to 9~AM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.9cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/16.pdf}
           {\\(e) 4~PM to 5~PM}
         \end{minipage}
   \end{minipage}
   \hspace{3mm}
   \begin{minipage}[b]{0.3\linewidth}
   \centering
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/4.pdf}
           {\\(b) 4~AM to 5~AM}
         \end{minipage}
         %\hspace{3mm}
         \begin{minipage}[b]{\linewidth}
           \centering
           \hspace*{-0.1cm}
           \includegraphics[width=42mm]{car2go_heatmaps/min/12.pdf}
           {\\(d) 12~AM to 1~PM}
         \end{minipage}
         \begin{minipage}[b]{\linewidth}
           \hspace*{-0.1cm}
           \centering
           \includegraphics[width=42mm]{car2go_heatmaps/min/20.pdf}
           {\\(f) 8~PM to 9~PM}
         \end{minipage}
   \end{minipage}
   \begin{minipage}[b]{0.1\linewidth}
   \centering
   		 \hspace*{12mm}
   		 \includegraphics[width=12mm]{car2go_heatmaps/legenda_car2go.pdf}
         \vspace{17mm}
   \end{minipage}
   %\hspace{1cm}
   \caption{Spatial-temporal service demand for free-floating service Car2Go.}
   \label{fig:4_4_heat_car2go}
\end{figure}

Figures~\ref{fig:4_4_heat_modo}, \ref{fig:4_4_heat_evo} and \ref{fig:4_4_heat_car2go} present heat-maps of the hourly\footnote{Due to space constraints, we only show one-hour period every four hour.} mean number of busy vehicles in a given location, considering analyzed period. In the case of Modo, a location refers to a fixed station. In the case of the other two services, the maps present clustered travel records where users pick-up or leave a vehicle. To cluster these points the algorithm uses a 400\,m radius as a reference, forming a region close to a neighborhood. Rangin radius from 100\,m to 1000\,m, leads to similar results.

@@

Figures~\ref{fig:4_4_matrixEvo} and \ref{fig:4_4_matrixCar2Go} detail the spatial-temporal demand for Evo and Car2Go by presenting their origin-destination matrix mapped on 31 city areas as defined by the metropolitan city of Vancouver. To enhance the visual effects, we normalized the previous heat-maps values to a scale between 0-1, using the min-max method. Moreover, due to space constraint, this work shows the origin-destination matrix at a specific hour, i.e., at 4\,PM.
In general, the users tend to start and end a trip at the same location. It appears that during working days, users tend to use a shared car  returning it to the same region where they start (likely where they are working or living). However, for both services, a non-negligible probability to spread services along all city area is noticeable. 
Moreover, we also note that some regions serve as hubs. This is more notable for Evo service. As shown in figure~\ref{fig:4_4_matrixEvo}, the downtown area serves as a hub to start trips to almost all other regions. The opposite (a high tendency to start a trip ending at downtown) trend is not present. As a consequence, service may become unbalanced and, from time to time, service maintenance should relocate vehicles from a region to another, to accommodate the daily demand.

\begin{figure}[tbh]
\centering
\includegraphics[width=0.85\columnwidth]{destination_matrix/hour16.png}
\caption{Origin-destination matrix for one-way service Evo (from 4~PM to 5~PM).}
\label{fig:4_4_matrixEvo}
\end{figure}
%
\begin{figure}[tbh]
\centering
\includegraphics[width=0.85\columnwidth]{car2go_destination_matrix/hour16.png}
\caption{Origin-destination matrix for free-floating service Car2Go (from 4~PM to 5~PM).}
\label{fig:4_4_matrixCar2Go}
\end{figure}

@@

\subsection{User behavior characteristics}
\label{sec:4_4_user-behavior}

@@

Figure~\ref{fig:4_4_busy_all_eCDF} shows the Cumulative Distribution Function of vehicle busy time.  Modo, Evo and Car2Go busy time and their best statistical distribution fitting are shown in blue, red and yellow, respectively. For all three services, the Inverse~Gamma\footnote{Cumulative distribution function (CDF) of the Inverse~Gamma distribution: $F(x, a, \beta, \delta) = \frac{1}{\Gamma(a)}\int_{1/\left((x-\beta)/\delta\right)}^{\infty}t^{a-1}e^{-t}dt$}, 
the Burr\footnote{Cumulative distribution function (CDF) of the Burr distribution: $F(x,c,d,\beta,\delta)=\left(1 + \left((x-\beta)/\delta\right)^{-c}\right)^{-d}$}, 
and Mielke's Beta-Kappa\footnote{Cumulative distribution function (CDF) of the Mielke's Beta-Kappa distribution: $F(x,k,s,\beta,\delta) = \frac{\left((x-\beta)/\delta\right)^{k}}{(1+\left((x-\beta)/\delta\right)^{s})^{(k*\frac{1}{s})}}$} 
distributions present a  good fitting to the empirical data, with similar MLEs.  
Table~\ref{table:fit_busy} summarizes the parameters of the distributions of the busy time for each statistical distribution.
Despite all three services present the same statistical distribution fitting, 
the two-way service (i.e., Modo), presents a clear shift to right on its curve when compared to the other two services, as shown in Figure~\ref{fig:4_4_busy_all_eCDF}. As we previously discussed, the median busy time on Modo is more than one hour longer than the median busy time for the other services. 
Users in Modo must return cars to the same station they originated travels. As a consequence, they tend to perform longer tasks. On the other hand, with the other two services users tend to do a longer number of shorter travels.

Finally, figure~\ref{fig:4_4_idle_all_eCDF}, presents vehicle idle periods distribution.  Power~log~normal\footnote{Cumulative distribution function (CDF) of the Power~log~normal distribution: $F(x,c,s,\beta,\delta)=1-\left(\frac{1}{\sqrt{2\pi}}\int_{-\infty}^{-log((x-\beta)/\delta)/s}e^{-t^{2}/2}dt\right)^{c}$}, Burr and Mielke's~Beta$-$Kappa distributions best fit the idle data, for all three datasets. Table~\ref{table:fit_idle} presents the distribution parameters. 
Again, Modo presents a distinct behavior from the other two services. The longer idle period for Modo vehicles corroborates to our previous observations. Indeed, the demand for car-sharing varies over the city during a day. While users in Evo and Car2Go can park anywhere, they contribute to spreading cars over the city. For example, at least 75\% of cars in Modo remains idle for periods longer than 2 hours. For the other two services, no more than 20\% of vehicles remains idle for the same period.

@@

\begin{figure}[tbh]
   \centering
   \includegraphics[width=0.85\columnwidth]{images_test/CDF_Fit_final.pdf}
   \caption{Cumulative distribution function of vehicle busy time.}
   \label{fig:4_4_busy_all_eCDF}
\end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=0.85\columnwidth]{images_test/CDF_Fit_idle_final.pdf}
   \caption{Cumulative distribution function of vehicle idle time}
   \label{fig:4_4_idle_all_eCDF}
\end{figure}

### 2020-10-29 Chapter4/4_6_conclusion.tex
chapter_4_passed

In this article, we characterized three distinct car-sharing systems which operate in  Vancouver  (Canada)  and nearby regions. Our study, using data of more than one year of real trips, uncovers patterns of users’ habits.  We provided a characterization of the different car-sharing services, including spatial-temporal usage. Finally, we highlighted the main differences and the common characteristics of these services.

The analyses points out how, in Vancouver in 2017 the one-way and free-floating services were used similarly. They present shorter travels when compared to the two-way service. All three services present peaks of demand during the day. During working days, these peaks occur at around 8\,AM and 6\,PM, while in weekends, peaks are distributed in the afternoon. The two-way service we analyze presents a considerable number of booking cancellations and a higher vehicle idle time. This indicates a low utilization of the vehicles, likely due to their business model. Indeed, one-way and free-floating services allow users to pick-up a car and leave it anywhere in the city, dynamically satisfying the floating demand. 
A strong relationship with the public transportation system, as well as with points of interests such as public universities and commercial centers is present.

>>>>

This chapter characterizes three distinct car-sharing systems which operate in  Vancouver  (Canada)  and nearby regions. The study, using data of more than one year of real trips, uncovers patterns of users’ habits. We provided a characterization of the different car-sharing services, including spatial-temporal usage. Finally, we highlighted the main differences and the common characteristics of these services.

The analyses point out how, in Vancouver in 2017 the one-way and free-floating services were used similarly. They present shorter travels when compared to the two-way service. All three services present peaks of demand during the day. During working days, these peaks occur at around 8\,AM and 6\,PM, while in weekends, peaks are distributed in the afternoon. The analyzed two-way service, presents a considerable number of booking cancellations and a higher vehicle idle time. This indicates a low utilization of the vehicles, likely due to their business model. Indeed, one-way and free-floating services allow users to pick-up a car and leave it anywhere in the city, dynamically satisfying the floating demand. 
A strong relationship with the public transportation system, as well as with points of interests such as public universities and commercial centers is present.
